Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-30 Ch1_movement_rates/Ch1_Figures.Rmd
Updated figure 5 to include half of the curves.
Added lines to guide the tails in Figure 5. Also using the 1000 estimates now.

xmax <- 1500
ncurves <- 200

@@

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> pp.dens

@@

cp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> pp.tail

np.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> np.tail

>>>>

xmax <- 1500
ncurves <- 1000

@@

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "") +
  theme(panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "") +
  theme(panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> pp.dens

@@

cp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "grey")) +
  geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
  labs(y = "") -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "grey")) +
    geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
  labs(y = "") -> pp.tail

np.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "grey")) +
    geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
  labs(y = "") -> np.tail
